География названий юридических фирм в России

### 2025-02-10 law-firms-names/conference-paper/Conference-slides.qmd
Use parquet to store large datasets instead of csv, add and commit large datasets

library(dplyr)
library(ggplot2)
library(here)
library(knitr)
library(readr)
library(sf)
library(spatstat)
library(stringr)
library(tidyr)
```

@@

# load the data
data <- read_csv(here("common", "panel.csv"))
cluster_labels <- read_csv(
  here("conference-paper", "cluster-labels-conf.csv"))
vectors <- read_csv(here("common", "names-vectors.csv"))
ru <- st_read(here("common", "ru.geojson"))

>>>>

library(dplyr)
library(ggplot2)
library(here)
library(knitr)
library(nanoparquet)
library(readr)
library(sf)
library(spatstat)
library(stringr)
library(tidyr)
```

@@

# load the data
data <- read_parquet(here("../datasets/law-firms/panel.parquet"))
cluster_labels <- read_csv(
  here("conference-paper/assets/cluster-labels-conf.csv"))
vectors <- read_parquet(here("common/names-vectors.parquet"))
ru <- st_read(here("common/regions.geojson"))
